---
title: "Estimation of population models of interest in R using the nlme package"
authors: "Ginette Lafit (ginette.lafit@kuleuven.be)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries

### Prelim - Installing libraries used in this script (whenever is necessary).

```{r, echo=TRUE, warning=TRUE, results="hide", message=FALSE}
# This code chunk simply makes sure that all the 
# libraries used here are installed.
packages <- c("nlme", "tidyr", "foreign", "data.table")
if ( length(missing_pkgs <- setdiff(packages, 
  rownames(installed.packages()))) > 0) {
  message("Installing missing package(s): ", 
          paste(missing_pkgs, collapse = ", "))
  install.packages(missing_pkgs)
}
```

### Prelim - Loading libraries used in this script.

```{r}
library(nlme) # to estimate linear-mixed effect models
library(tidyverse) # reshaped data and variable transformation
library(foreign) # load .sav data set
library(data.table) # to create lagged outcome
```

## Data preprocessing

For a given data set, we create the lagged outcome variable, person-mean centered the predictors, and create a predictor X^2:

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Create lag outcome
data.dyad$Y.lag = rep(0,nrow(data.dyad))
n.subject = unique(data.dyad$subject.ID)
for (j in n.subject){
data.dyad$Y.lag[which(data.dyad$subject.ID==j)] = shift(data.dyad$Y[which(data.dyad$subject.ID==j)])
}

# Person-mean centered the predictors
data.dyad <- data.dyad %>% 
group_by(subject.ID,dyad.ID) %>% 
mutate(X.Actor.c = X.Actor - mean(X.Actor,na.rm = TRUE),
       X.Partner.c = X.Partner - mean(X.Partner,na.rm = TRUE))

# Compute quadratic variable
data.dyad$X.Actor.c.2 = I(data.dyad$X.Actor.c^2)
data.dyad$X.Partner.c.2 = I(data.dyad$X.Partner.c^2)
```

## Model estimation

### Model 1: APIM 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.1 = lme(fixed = Y ~ -1 + Female + Female:X.Actor.c + 
                  Female:X.Partner.c + Male + 
                  Male:X.Actor.c + Male:X.Partner.c,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data.dyad, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = FALSE))  

summary(fit.Model.1)
```

### Model 2: APIM for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.2 = lme(fixed = Y ~ 1 + X.Actor.c + X.Partner.c,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data.dyad, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = FALSE)) 

summary(fit.Model.2)
```


### Model 3: Group differences in the actor and partner effects 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z

# Model estimation

fit.Model.3 = lme(fixed = Y ~ -1 + Female + Female.Z + 
              Female:X.Actor.c + Female:X.Actor.c.Z + 
              Female:X.Partner.c + Female:X.Partner.c.Z + 
              Male + Male.Z + Male:X.Actor.c + Male:X.Actor.c.Z + 
              Male:X.Partner.c + Male:X.Partner.c.Z,
              random = ~ -1 + Female + Male |dyad.ID, 
              correlation = corCompSymm(form = ~1|dyad.ID/Obs),
              weights = varIdent(form = ~1|Gender),
              data = data, na.action=na.omit, 
              control = lmeControl(optimizer="bobyqa", 
                                   optCtrl=list(maxfun=2e5), 
              maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.3)
```

### Model 4: Group differences in the actor and partner effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z

# Model estimation

fit.Model.4 = lme(fixed = Y ~ 1 + Z + X.Actor.c + X.Actor.c.Z + 
                  X.Partner.c + X.Partner.c.Z,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.4)
```

### Model 5: Continuous time-varying moderator 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.C = data$X.Actor.c*data$C
data$X.Partner.c.C = data$X.Partner.c*data$C

# Model estimation

fit.Model.5 = lme(fixed = Y ~ -1 + Female + 
                  Female:X.Actor.c + Female:X.Partner.c +
                  Female:C + Female:X.Actor.c.C + 
                  Female:X.Partner.c.C + Male + 
                  Male:X.Actor.c + Male:X.Partner.c + Male:C + 
                  Male:X.Actor.c.C + Male:X.Partner.c.C,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.5)
```

### Model 6: Continuous time-varying moderator C for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.C = data$X.Actor.c*data$C
data$X.Partner.c.C = data$X.Partner.c*data$C

# Model estimation

fit.Model.6 = lme(fixed = Y ~ 1 + X.Actor.c + X.Partner.c +
                  C + X.Actor.c.C  + X.Partner.c.C,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.6)
```

### Model 7: Dichotomous time-varying moderator D 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.D = data$X.Actor.c*data$D
data$X.Partner.c.D = data$X.Partner.c*data$D

# Model estimation

fit.Model.7 = lme(fixed = Y ~ -1 + Female + 
                  Female:X.Actor.c + Female:X.Partner.c +
                  Female:D + Female:X.Actor.c.D + Female:X.Partner.c.D + 
                  Male + Male:X.Actor.c + Male:X.Partner.c + Male:D + 
                  Male:X.Actor.c.D + Male:X.Partner.c.D,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.7)
```

### Model 8: Dichotomous time-varying moderator D for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.D = data$X.Actor.c*data$D
data$X.Partner.c.W = data$X.Partner.c*data$D

# Model estimation

fit.Model.8 = lme(fixed = Y ~ 1 + X.Actor.c + X.Partner.c +
                  D + X.Actor.c.D  + X.Partner.c.D,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.8)
```

### Model 9: APIM with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.9 = lme(fixed = Y ~ -1 + Female + 
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 + Male + 
                  Male:X.Actor.c + Male:X.Actor.c.2 + Male:X.Partner.c + 
                  Male:X.Partner.c.2,
                  random = ~ -1 + Female + Male |dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data.dyad, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = FALSE)) 

summary(fit.Model.9)
```

### Model 10: APIM with curvilinear effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.10 = lme(fixed = Y ~ 1 + X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data.dyad, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = FALSE)) 

summary(fit.Model.10)
```


### Model 11: Group differences in the actor and partner effects with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$X.Actor.c.2.Z = data$X.Actor.c.2*data$Z
data$X.Partner.c.2.Z = data$X.Partner.c.2*data$Z

# Model estimation

fit.Model.11 = lme(fixed = Y ~ -1 + Female + Female.Z + 
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Actor.c.Z + Female:X.Actor.c.2.Z + 
                  Female:X.Partner.c +  Female:X.Partner.c.2 + 
                  Female:X.Partner.c.Z + Female:X.Partner.c.2.Z + 
                  Male + Male.Z + 
                  Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Actor.c.Z + + Male:X.Actor.c.2.Z + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:X.Partner.c.Z + Male:X.Partner.c.2.Z,
                  random = ~ -1 + Female + Male |dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  msMaxIter = 100, msVerbose = TRUE))

summary(fit.Model.11)
```

### Model 12: Group differences in the actor and partner effects with curvilinear effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$X.Actor.c.2.Z = data$X.Actor.c.2*data$Z
data$X.Partner.c.2.Z = data$X.Partner.c.2*data$Z

# Model estimation

fit.Model.12 = lme(fixed = Y ~ 1 + Z  + 
                  X.Actor.c + X.Actor.c.2 + 
                  X.Actor.c.Z + X.Actor.c.2.Z + 
                  X.Partner.c + X.Partner.c.2 + 
                  X.Partner.c.Z + X.Partner.c.2.Z,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.12)
```

### Model 13: Continuous time-varying moderator C with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.C.c = data$X.Actor.c*data$C.c
data$X.Partner.C.c = data$X.Partner.c*data$C.c
data$X.Actor.C.c.2 = data$X.Actor.c.2*data$C.c
data$X.Partner.C.c.2 = data$X.Partner.c.2*data$C.c

# Model estimation

fit.Model.13 = lme(fixed = Y ~ -1 + Female + 
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 +
                  Female:C.c + Female:X.Actor.C.c + Female:X.Actor.C.c.2 +
                  Female:X.Partner.C.c + Female:X.Partner.C.c.2 + 
                  Male + Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:C.c + Male:X.Actor.C.c + Male:X.Actor.C.c.2 + 
                  Male:X.Partner.C.c + Male:X.Partner.C.c.2,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.13)
```

### Model 14: Continuous time-varying dyad moderator with curvilinear effects for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.C.c = data$X.Actor.c*data$C.c
data$X.Partner.C.c = data$X.Partner.c*data$C.c
data$X.Actor.C.c.2 = data$X.Actor.c.2*data$C.c
data$X.Partner.C.c.2 = data$X.Partner.c.2*data$C.c

# Model estimation

fit.Model.14 = lme(fixed = Y ~ 1 + X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2 +
                  C.c + X.Actor.C.c + X.Actor.C.c.2 +
                  X.Partner.C.c + X.Partner.C.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.14)
```

### Model 15: Dichotomous time-varying moderator D with curvilinear effects 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.D.c = data$X.Actor.c*data$D.c
data$X.Partner.D.c = data$X.Partner.c*data$D.c
data$X.Actor.D.c.2 = data$X.Actor.c.2*data$D.c
data$X.Partner.D.c.2 = data$X.Partner.c.2*data$D.c

# Model estimation

fit.Model.15 = lme(fixed = Y ~ -1 + Female + 
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 +
                  Female:D.c + Female:X.Actor.D.c + Female:X.Actor.D.c.2 +
                  Female:X.Partner.D.c + Female:X.Partner.D.c.2 + 
                  Male + Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:D.c + Male:X.Actor.D.c + Male:X.Actor.D.c.2 + 
                  Male:X.Partner.D.c + Male:X.Partner.D.c.2,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.15)
```

### Model 16: Dichotomous time-varying moderator D with curvilinear effects for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.D.c = data$X.Actor.c*data$D.c
data$X.Partner.D.c = data$X.Partner.c*data$D.c
data$X.Actor.D.c.2 = data$X.Actor.c.2*data$D.c
data$X.Partner.D.c.2 = data$X.Partner.c.2*data$D.c

# Model estimation

fit.Model.16 = lme(fixed = Y ~ 1 + X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2 +
                  D.c + X.Actor.D.c + X.Actor.D.c.2 +
                  X.Partner.D.c + X.Partner.D.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.16)
```


### Model 17: APIM 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.17 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag +
                  Female:X.Actor.c + Female:X.Partner.c + 
                  Male + Male:Y.lag +
                  Male:X.Actor.c + Male:X.Partner.c,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.17)
```

### Model 18: APIM for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.18 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Partner.c,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.18)
```


### Model 19: Group differences in the actor and partner effects 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$Y.lag.Z = data$Y.lag*data$Z

# Model estimation

fit.Model.19 = lme(fixed = Y ~ -1 + Female + Female:Y.lag + 
              Female:Y.lag.Z + Female.Z + 
              Female:X.Actor.c + Female:X.Actor.c.Z + 
              Female:X.Partner.c + Female:X.Partner.c.Z + 
              Male + Male.Z + 
              Male:Y.lag + Male:Y.lag.Z + 
              Male:X.Actor.c + Male:X.Actor.c.Z + 
              Male:X.Partner.c + Male:X.Partner.c.Z,
              random = ~ -1 + Female + Male |dyad.ID, 
              correlation = corCompSymm(form = ~1|dyad.ID/Obs),
              weights = varIdent(form = ~1|Gender),
              data = data, na.action=na.omit, 
              control = lmeControl(optimizer="bobyqa", 
                                   optCtrl=list(maxfun=2e5), 
              maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.19)
```

### Model 20: Group differences in the actor and partner effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$Y.lag.Z = data$Y.lag*data$Z

# Model estimation

fit.Model.20 = lme(fixed = Y ~ 1 + Z + 
                  Y.lag + Y.lag.Z +
                  X.Actor.c + X.Actor.c.Z + 
                  X.Partner.c + X.Partner.c.Z,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.20)
```

### Model 21: Continuous time-varying moderator C

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.C = data$X.Actor.c*data$C
data$X.Partner.c.C = data$X.Partner.c*data$C

# Model estimation

fit.Model.21 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag +
                  Female:X.Actor.c + Female:X.Partner.c +
                  Female:C + Female:X.Actor.c.C + Female:X.Partner.c.C + 
                  Male + Male:Y.lag +
                  Male:X.Actor.c + Male:X.Partner.c + Male:C + 
                  Male:X.Actor.c.C + Male:X.Partner.c.C,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.21)
```

### Model 22: Continuous time-varying moderator C for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.C = data$X.Actor.c*data$C
data$X.Partner.c.C = data$X.Partner.c*data$C

# Model estimation

fit.Model.22 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Partner.c +
                  C + X.Actor.c.C  + X.Partner.c.C,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.22)
```

### Model 23: Dichotomous time-varying moderator D 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.D = data$X.Actor.c*data$D
data$X.Partner.c.D = data$X.Partner.c*data$D

# Model estimation

fit.Model.23 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag + 
                  Female:X.Actor.c + Female:X.Partner.c +
                  Female:D + Female:X.Actor.c.D + Female:X.Partner.c.D + 
                  Male + Male:Y.lag + 
                  Male:X.Actor.c + Male:X.Partner.c + Male:D + 
                  Male:X.Actor.c.D + Male:X.Partner.c.D,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.23)
```

### Model 24: Dichotomous time-varying moderator D for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.c.D = data$X.Actor.c*data$D
data$X.Partner.c.W = data$X.Partner.c*data$D

# Model estimation

fit.Model.24 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Partner.c +
                  D + X.Actor.c.D  + X.Partner.c.D,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.24)
```

### Model 25: APIM with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.25 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag +
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 + 
                  Male + Male:Y.lag + 
                  Male:X.Actor.c + Male:X.Actor.c.2 + Male:X.Partner.c + 
                  Male:X.Partner.c.2,
                  random = ~ -1 + Female + Male |dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.25)
```

### Model 26: APIM with curvilinear effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
fit.Model.26 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.26)
```


### Model 27: Group differences in the actor and partner effects with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$X.Actor.c.2.Z = data$X.Actor.c.2*data$Z
data$X.Partner.c.2.Z = data$X.Partner.c.2*data$Z

# Model estimation

fit.Model.27 = lme(fixed = Y ~ -1 + Female + Female.Z +
                  Female:Y.lag + Female:Y.lag.Z +
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Actor.c.Z + Female:X.Actor.c.2.Z + 
                  Female:X.Partner.c +  Female:X.Partner.c.2 + 
                  Female:X.Partner.c.Z + Female:X.Partner.c.2.Z + 
                  Male + Male.Z + 
                  Male:Y.lag + Male:Y.lag.Z +
                  Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Actor.c.Z + + Male:X.Actor.c.2.Z + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:X.Partner.c.Z + Male:X.Partner.c.2.Z,
                  random = ~ -1 + Female + Male |dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  msMaxIter = 100, msVerbose = TRUE))

summary(fit.Model.27)
```

### Model 28: Group differences in the actor and partner effects with curvilinear effects for indistinguishable dyads 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$Female.Z = data$Female*data$Z
data$Male.Z = data$Male*data$Z
data$X.Actor.c.Z = data$X.Actor.c*data$Z
data$X.Partner.c.Z = data$X.Partner.c*data$Z
data$X.Actor.c.2.Z = data$X.Actor.c.2*data$Z
data$X.Partner.c.2.Z = data$X.Partner.c.2*data$Z

# Model estimation

fit.Model.28 = lme(fixed = Y ~ 1 + Z  +
                  Y.lag + Y.lag.Z +
                  X.Actor.c + X.Actor.c.2 + 
                  X.Actor.c.Z + X.Actor.c.2.Z + 
                  X.Partner.c + X.Partner.c.2 + 
                  X.Partner.c.Z + X.Partner.c.2.Z,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.28)
```

### Model 29: Continuous time-varying moderator C with curvilinear effects

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.C.c = data$X.Actor.c*data$C.c
data$X.Partner.C.c = data$X.Partner.c*data$C.c
data$X.Actor.C.c.2 = data$X.Actor.c.2*data$C.c
data$X.Partner.C.c.2 = data$X.Partner.c.2*data$C.c

# Model estimation

fit.Model.29 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag + 
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 +
                  Female:W.c + Female:X.Actor.C.c + Female:X.Actor.C.c.2 +
                  Female:X.Partner.C.c + Female:X.Partner.C.c.2 + 
                  Male + Male:Y.lag + 
                  Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:C.c + Male:X.Actor.C.c + Male:X.Actor.C.c.2 + 
                  Male:X.Partner.C.c + Male:X.Partner.C.c.2,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.29)
```

### Model 30: Continuous time-varying moderator C with curvilinear effects for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.C.c = data$X.Actor.c*data$C.c
data$X.Partner.C.c = data$X.Partner.c*data$C.c
data$X.Actor.C.c.2 = data$X.Actor.c.2*data$C.c
data$X.Partner.C.c.2 = data$X.Partner.c.2*data$C.c

# Model estimation

fit.Model.30 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2 +
                  C.c + X.Actor.C.c + X.Actor.C.c.2 +
                  X.Partner.C.c + X.Partner.C.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.30)
```

### Model 31: Dichotomous time-varying moderator D with curvilinear effects 

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.D.c = data$X.Actor.c*data$D.c
data$X.Partner.D.c = data$X.Partner.c*data$D.c
data$X.Actor.D.c.2 = data$X.Actor.c.2*data$D.c
data$X.Partner.D.c.2 = data$X.Partner.c.2*data$D.c

# Model estimation

fit.Model.31 = lme(fixed = Y ~ -1 + 
                  Female + Female:Y.lag +
                  Female:X.Actor.c + Female:X.Actor.c.2 + 
                  Female:X.Partner.c + Female:X.Partner.c.2 +
                  Female:D.c + Female:X.Actor.D.c + Female:X.Actor.D.c.2 +
                  Female:X.Partner.D.c + Female:X.Partner.D.c.2 + 
                  Male + Male:Y.lag +
                  Male:X.Actor.c + Male:X.Actor.c.2 + 
                  Male:X.Partner.c + Male:X.Partner.c.2 + 
                  Male:D.c + Male:X.Actor.D.c + Male:X.Actor.D.c.2 + 
                  Male:X.Partner.D.c + Male:X.Partner.D.c.2,
                  random = ~ -1 + Female + Male|dyad.ID, 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE)) 

summary(fit.Model.31)
```

### Model 32: Dichotomous time-varying moderator D with curvilinear effects for indistinguishable dyads

```{r, echo=TRUE, warning=FALSE, eval=FALSE}
# Compute interactions
data$X.Actor.D.c = data$X.Actor.c*data$D.c
data$X.Partner.D.c = data$X.Partner.c*data$D.c
data$X.Actor.D.c.2 = data$X.Actor.c.2*data$D.c
data$X.Partner.D.c.2 = data$X.Partner.c.2*data$D.c

# Model estimation

fit.Model.32 = lme(fixed = Y ~ 1 + Y.lag +
                  X.Actor.c + X.Actor.c.2 + 
                  X.Partner.c + X.Partner.c.2 +
                  D.c + X.Actor.D.c + X.Actor.D.c.2 +
                  X.Partner.D.c + X.Partner.D.c.2,
                  random = list(dyad.ID = pdCompSymm(~ Gender -1)), 
                  correlation = corCompSymm(form = ~1|dyad.ID/Obs),
                  weights = varIdent(form = ~1|Gender),
                  data = data, na.action=na.omit, 
                  control = lmeControl(optimizer="bobyqa", 
                                       optCtrl=list(maxfun=2e5), 
                  maxIter=500, msMaxIter=500, msVerbose = TRUE))

summary(fit.Model.32)
```

