---
title: "Validating Power Analysis using PowerLAPIM and SEM"
author: 'Ginette Lafit (ginette.lafit@kuleuven.be)'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries

### Prelim - Installing libraries used in this script (whenever is necessary).

```{r, echo=TRUE, warning=TRUE, results="hide", message=FALSE}
# This code chunk simply makes sure that all the 
# libraries used here are installed.
# Check if R packages are installed

list.of.packages = c("nlme","MASS","tidyverse","future.apply","gridExtra","formattable",
"htmltools","shiny","DT","ggplot2","gridExtra","data.table","plyr","dplyr",
"tidyr","shinyjs","reshape","lavaan","kableExtra")
new.packages = list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Delet # if the package PowerLAPIM is not installed yet
#library(devtools)
#devtools::install_github("ginettelafit/PowerLAPIM", force = T)
```

### Prelim - Loading libraries used in this script.

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Load packages
library(nlme)
library(MASS)
library(tidyverse)
library(future.apply)
library(gridExtra)
library(formattable)
library(htmltools)
library(shiny)
library(DT)
library(ggplot2)
library(gridExtra)
library(data.table)
library(plyr)
library(dplyr)
library(tidyr)
library(shinyjs)
library(PowerLAPIM)
library(reshape)
library(lavaan)
library(foreign)
library(kableExtra)
```


To validate the results obtained with PowerLAPIM, we compare two modeling approaches to analyze the L-APIM with linear effects: the multilevel approach using the application and structural equation modeling (SEM).

We applied Model 1: L-APIM with linear effect only to the Dyadic Interaction data to estimate actor and partner effects of partners’ enacted responsiveness on their happiness. For each participant, we select the first 10 time points, and we estimate Model 1 using SEM. We set the correlation between the partners’ enacted responsiveness to zero. We also assume that the correlation between the Level 1 errors is zero. 

## Data preprocessing for SEM analysis

First, we preprocessed and re-shaped the data from the Dyadic Interaction study. Because the ESM data is in the long format, we have to converte it to the wide format to estimate the L-APIM using SEM. 

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Load person period data set
data.person = read.spss("ESM_8.sav", to.data.frame=TRUE)
data.person = data.frame(data.person)

# Select variable to use 
data.person = data.person[,c('couple','ppnr','beepnr','DayESM','happy','enact_respons')]

# Select the first 10 beeps
data.person = data.person[data.person$beepnr<=10,]

# create variable Gender
data.person$Gender = ifelse(data.person$ppnr == data.person$couple,'F','M')

# Select data for the Female partner
data.person.F = data.person[data.person$Gender=='F',]
data.person.F = data.person.F[,c('couple','ppnr','beepnr','happy','enact_respons')]
colnames(data.person.F) = c('couple_F','ppnr_F','beepnr','YF','XF')
data.person.F.wide = reshape(data.person.F, idvar = c('couple_F','ppnr_F'), timevar = "beepnr", direction = "wide")

# Select data for the Male partner
data.person.M = data.person[data.person$Gender=='M',]
data.person.M = data.person.M[,c('couple','ppnr','beepnr','happy','enact_respons')]
colnames(data.person.M) = c('couple_M','ppnr_M','beepnr','YM','XM')
data.person.M.wide = reshape(data.person.M, idvar = c('couple_M','ppnr_M'), timevar = "beepnr", direction = "wide")

# Combine wide data sets
data.person.wide = cbind(data.person.F.wide,data.person.M.wide)
# Data check
sum(data.person.wide$couple_F == data.person.wide$couple_M) - nrow(data.person.wide)

# Eliminate rows with Nas
data.person.wide = data.person.wide[complete.cases(data.person.wide), ]

# Centered the predictors
data.person.wide.center = data.person.wide[,c("XF.1","XF.2","XF.3","XF.4","XF.5","XF.6","XF.7","XF.8","XF.9","XF.10","XM.1","XM.2","XM.3","XM.4","XM.5","XM.6","XM.7","XM.8","XM.9","XM.10")] -  rowMeans(data.person.wide[,c("XF.1","XF.2","XF.3","XF.4","XF.5","XF.6","XF.7","XF.8","XF.9","XF.10","XM.1","XM.2","XM.3","XM.4","XM.5","XM.6","XM.7","XM.8","XM.9","XM.10")])
colnames(data.person.wide.center) = c("XF.c.1","XF.c.2","XF.c.3","XF.c.4","XF.c.5","XF.c.6","XF.c.7","XF.c.8","XF.c.9","XF.c.10","XM.c.1","XM.c.2","XM.c.3","XM.c.4","XM.c.5","XM.c.6","XM.c.7","XM.c.8","XM.c.9","XM.c.10")

# Obtain data set with centered predictors
data.person.wide = cbind(data.person.wide,data.person.wide.center)

```

### Summary predictors

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Distribution of the predictors X
# Female partner
mu.XF = mean(data.person$enact_respons[which(data.person$Gender=='F')],na.rm = TRUE)
mu.XF
sigma.XF = sd(data.person$enact_respons[which(data.person$Gender=='F')],na.rm = TRUE)
sigma.XF
sigma2.XF = var(data.person$enact_respons[which(data.person$Gender=='F')],na.rm = TRUE)
sigma2.XF
# Male partner
mu.XM = mean(data.person$enact_respons[which(data.person$Gender=='M')],na.rm = TRUE)
mu.XM
sigma.XM = sd(data.person$enact_respons[which(data.person$Gender=='M')],na.rm = TRUE)
sigma.XM
sigma2.XM = var(data.person$enact_respons[which(data.person$Gender=='M')],na.rm = TRUE)
sigma2.XM

```

### We first estimate L-APIM using SEM

We applied Model 1: L-APIM with linear effect only to the Dyadic Interaction data to estimate actor and partner effects of partners’ enacted responsiveness on their happiness. For each participant, we select the first 10 time points, and we estimate Model 1 using SEM. We set the correlation between the partners’ enacted responsiveness to zero. We also assume that the correlation between the Level 1 errors is zero. We estimate the model using the ‘sem’ function from the lavaan package. 

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
## Estimate L-APIM based on multilevel model using lavaan
model_LAPIM_Fit = '

# random intercepts
i.M =~ 1*YM.1 + 1*YM.2 + 1*YM.3 + 1*YM.4 + 1*YM.5 + 1*YM.6 + 1*YM.7 + 1*YM.8 + 1*YM.9 + 1*YM.10 
i.F =~ 1*YF.1 + 1*YF.2 + 1*YF.3 + 1*YF.4 + 1*YF.5 + 1*YF.6 + 1*YF.7 + 1*YF.8 + 1*YF.9 + 1*YF.10 

# random covariance structure
i.M ~~ ivarA*i.M + iA*i.F
i.F ~~ ivarB*i.F

# mean structure: Predictors
XM.1 ~ mu.XM*1 
XM.2 ~ mu.XM*1 
XM.3 ~ mu.XM*1 
XM.4 ~ mu.XM*1 
XM.5 ~ mu.XM*1 
XM.6 ~ mu.XM*1 
XM.7 ~ mu.XM*1 
XM.8 ~ mu.XM*1 
XM.9 ~ mu.XM*1 
XM.10 ~ mu.XM*1 

XF.1 ~ mu.XF*1 
XF.2 ~ mu.XF*1 
XF.3 ~ mu.XF*1 
XF.4 ~ mu.XF*1 
XF.5 ~ mu.XF*1 
XF.6 ~ mu.XF*1 
XF.7 ~ mu.XF*1 
XF.8 ~ mu.XF*1 
XF.9 ~ mu.XF*1
XF.10 ~ mu.XF*1 

# residual structure: Predictors
XM.1 ~~ varXM*XM.1
XM.2 ~~ varXM*XM.2
XM.3 ~~ varXM*XM.3
XM.4 ~~ varXM*XM.4
XM.5 ~~ varXM*XM.5
XM.6 ~~ varXM*XM.6
XM.7 ~~ varXM*XM.7
XM.8 ~~ varXM*XM.8
XM.9 ~~ varXM*XM.9
XM.10 ~~ varXM*XM.10

XF.1 ~~ varXF*XF.1
XF.2 ~~ varXF*XF.2
XF.3 ~~ varXF*XF.3
XF.4 ~~ varXF*XF.4
XF.5 ~~ varXF*XF.5
XF.6 ~~ varXF*XF.6
XF.7 ~~ varXF*XF.7
XF.8 ~~ varXF*XF.8
XF.9 ~~ varXF*XF.9
XF.10 ~~ varXF*XF.10

# mean structure: Outcomes
YM.1 ~ c.M*1 + a.MM*XM.1 + p.FM*XF.1 
YM.2 ~ c.M*1 + a.MM*XM.2 + p.FM*XF.2
YM.3 ~ c.M*1 + a.MM*XM.3 + p.FM*XF.3
YM.4 ~ c.M*1 + a.MM*XM.4 + p.FM*XF.4
YM.5 ~ c.M*1 + a.MM*XM.5 + p.FM*XF.5
YM.6 ~ c.M*1 + a.MM*XM.6 + p.FM*XF.6
YM.7 ~ c.M*1 + a.MM*XM.7 + p.FM*XF.7
YM.8 ~ c.M*1 + a.MM*XM.8 + p.FM*XF.8
YM.9 ~ c.M*1 + a.MM*XM.9 + p.FM*XF.9
YM.10 ~ c.M*1 + a.MM*XM.10 + p.FM*XF.10

YF.1 ~ c.F*1 + a.FF*XF.1  + p.MF*XM.1
YF.2 ~ c.F*1 + a.FF*XF.2  + p.MF*XM.2
YF.3 ~ c.F*1 + a.FF*XF.3  + p.MF*XM.3
YF.4 ~ c.F*1 + a.FF*XF.4  + p.MF*XM.4
YF.5 ~ c.F*1 + a.FF*XF.5  + p.MF*XM.5
YF.6 ~ c.F*1 + a.FF*XF.6  + p.MF*XM.6
YF.7 ~ c.F*1 + a.FF*XF.7  + p.MF*XM.7
YF.8 ~ c.F*1 + a.FF*XF.8  + p.MF*XM.8
YF.9 ~ c.F*1 + a.FF*XF.9  + p.MF*XM.9
YF.10 ~ c.F*1 + a.FF*XF.10  + p.MF*XM.10

# residual structure: Outcomes
YM.1 ~~ varM*YM.1
YM.2 ~~ varM*YM.2
YM.3 ~~ varM*YM.3
YM.4 ~~ varM*YM.4
YM.5 ~~ varM*YM.5
YM.6 ~~ varM*YM.6
YM.7 ~~ varM*YM.7
YM.8 ~~ varM*YM.8
YM.9 ~~ varM*YM.9
YM.10 ~~ varM*YM.10

YF.1 ~~ varF*YF.1
YF.2 ~~ varF*YF.2
YF.3 ~~ varF*YF.3
YF.4 ~~ varF*YF.4
YF.5 ~~ varF*YF.5
YF.6 ~~ varF*YF.6
YF.7 ~~ varF*YF.7
YF.8 ~~ varF*YF.8
YF.9 ~~ varF*YF.9
YF.10 ~~ varF*YF.10
'

# Estimate L-APIM using SEM
fit_LAPIM_Fit = sem(model_LAPIM_Fit,data = data.person.wide)
summary(fit_LAPIM_Fit)

```

# Simulate data from L-APIM using SEM

Taking the estimated parameters of Model 1 based on the Dyadic Interaction data, we use the lavaan function ‘simulateData’ to generate 1000 data sets considering the following number of dyads: 60, 80, 100, 160, 200, and 300. For each of these data sets we estimate the L-APIM using structural equation modeling. Empirical power is then calculated as the proportion of replications in which the parameters of interest were estimated as significantly different from zero (at a specified α level of .05). 

First, we write the model to simulate data from L-APIM:

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Set the model parameters
model_LAPIM_Parameters = '

# random intercepts
i.M =~ 1*YM.1 + 1*YM.2 + 1*YM.3 + 1*YM.4 + 1*YM.5 + 1*YM.6 + 1*YM.7 + 1*YM.8 + 1*YM.9 + 1*YM.10 
i.F =~ 1*YF.1 + 1*YF.2 + 1*YF.3 + 1*YF.4 + 1*YF.5 + 1*YF.6 + 1*YF.7 + 1*YF.8 + 1*YF.9 + 1*YF.10 

# random covariance structure
i.M ~~ 76.356*i.M + 30.684*i.F
i.F ~~ 101.541*i.F

# mean structure: Predictors
XM.1 ~ 74.689*1 
XM.2 ~ 74.689*1 
XM.3 ~ 74.689*1 
XM.4 ~ 74.689*1 
XM.5 ~ 74.689*1 
XM.6 ~ 74.689*1 
XM.7 ~ 74.689*1 
XM.8 ~ 74.689*1 
XM.9 ~ 74.689*1 
XM.10 ~ 74.689*1 

XF.1 ~ 74.922*1 
XF.2 ~ 74.922*1 
XF.3 ~ 74.922*1 
XF.4 ~ 74.922*1 
XF.5 ~ 74.922*1 
XF.6 ~ 74.922*1 
XF.7 ~ 74.922*1 
XF.8 ~ 74.922*1 
XF.9 ~ 74.922*1
XF.10 ~ 74.922*1 

# residual structure: Predictors
XM.1 ~~ 331.517*XM.1
XM.2 ~~ 331.517*XM.2
XM.3 ~~ 331.517*XM.3
XM.4 ~~ 331.517*XM.4
XM.5 ~~ 331.517*XM.5
XM.6 ~~ 331.517*XM.6
XM.7 ~~ 331.517*XM.7
XM.8 ~~ 331.517*XM.8
XM.9 ~~ 331.517*XM.9
XM.10 ~~ 331.517*XM.10

XF.1 ~~ 360.089*XF.1
XF.2 ~~ 360.089*XF.2
XF.3 ~~ 360.089*XF.3
XF.4 ~~ 360.089*XF.4
XF.5 ~~ 360.089*XF.5
XF.6 ~~ 360.089*XF.6
XF.7 ~~ 360.089*XF.7
XF.8 ~~ 360.089*XF.8
XF.9 ~~ 360.089*XF.9
XF.10 ~~ 360.089*XF.10

# mean structure: Outcomes
YM.1 ~ 40.682*1 + 0.279*XM.1 + 0.074*XF.1 
YM.2 ~ 40.682*1 + 0.279*XM.2 + 0.074*XF.2
YM.3 ~ 40.682*1 + 0.279*XM.3 + 0.074*XF.3
YM.4 ~ 40.682*1 + 0.279*XM.4 + 0.074*XF.4
YM.5 ~ 40.682*1 + 0.279*XM.5 + 0.074*XF.5
YM.6 ~ 40.682*1 + 0.279*XM.6 + 0.074*XF.6
YM.7 ~ 40.682*1 + 0.279*XM.7 + 0.074*XF.7
YM.8 ~ 40.682*1 + 0.279*XM.8 + 0.074*XF.8
YM.9 ~ 40.682*1 + 0.279*XM.9 + 0.074*XF.9
YM.10 ~ 40.682*1 + 0.279*XM.10 + 0.074*XF.10

YF.1 ~ 39.243*1 + 0.283*XF.1 + 0.061*XM.1 
YF.2 ~ 39.243*1 + 0.283*XF.2 + 0.061*XM.2
YF.3 ~ 39.243*1 + 0.283*XF.3 + 0.061*XM.3
YF.4 ~ 39.243*1 + 0.283*XF.4 + 0.061*XM.4
YF.5 ~ 39.243*1 + 0.283*XF.5 + 0.061*XM.5
YF.6 ~ 39.243*1 + 0.283*XF.6 + 0.061*XM.6
YF.7 ~ 39.243*1 + 0.283*XF.7 + 0.061*XM.7
YF.8 ~ 39.243*1 + 0.283*XF.8 + 0.061*XM.8
YF.9 ~ 39.243*1 + 0.283*XF.9 + 0.061*XM.9
YF.10 ~ 39.243*1 + 0.283*XF.10 + 0.061*XM.10

# residual structure: Outcomes
YM.1 ~~ 257.404*YM.1
YM.2 ~~ 257.404*YM.2
YM.3 ~~ 257.404*YM.3
YM.4 ~~ 257.404*YM.4
YM.5 ~~ 257.404*YM.5
YM.6 ~~ 257.404*YM.6
YM.7 ~~ 257.404*YM.7
YM.8 ~~ 257.404*YM.8
YM.9 ~~ 257.404*YM.9
YM.10 ~~ 257.404*YM.10

YF.1 ~~ 223.108*YF.1
YF.2 ~~ 223.108*YF.2
YF.3 ~~ 223.108*YF.3
YF.4 ~~ 223.108*YF.4
YF.5 ~~ 223.108*YF.5
YF.6 ~~ 223.108*YF.6
YF.7 ~~ 223.108*YF.7
YF.8 ~~ 223.108*YF.8
YF.9 ~~ 223.108*YF.9
YF.10 ~~ 223.108*YF.10
'
```

Next, we write the model to estimate L-APIM:

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
## Estimate L-APIM based on multilevel model using lavaan
model_LAPIM = '

# random intercepts
i.M =~ 1*YM.1 + 1*YM.2 + 1*YM.3 + 1*YM.4 + 1*YM.5 + 1*YM.6 + 1*YM.7 + 1*YM.8 + 1*YM.9 + 1*YM.10 
i.F =~ 1*YF.1 + 1*YF.2 + 1*YF.3 + 1*YF.4 + 1*YF.5 + 1*YF.6 + 1*YF.7 + 1*YF.8 + 1*YF.9 + 1*YF.10 

# random covariance structure
i.M ~~ ivarA*i.M + iA*i.F
i.F ~~ ivarB*i.F

# mean structure: Outcomes
YM.1 ~ c.M*1 + a.MM*XM.1 + p.FM*XF.1 
YM.2 ~ c.M*1 + a.MM*XM.2 + p.FM*XF.2
YM.3 ~ c.M*1 + a.MM*XM.3 + p.FM*XF.3
YM.4 ~ c.M*1 + a.MM*XM.4 + p.FM*XF.4
YM.5 ~ c.M*1 + a.MM*XM.5 + p.FM*XF.5
YM.6 ~ c.M*1 + a.MM*XM.6 + p.FM*XF.6
YM.7 ~ c.M*1 + a.MM*XM.7 + p.FM*XF.7
YM.8 ~ c.M*1 + a.MM*XM.8 + p.FM*XF.8
YM.9 ~ c.M*1 + a.MM*XM.9 + p.FM*XF.9
YM.10 ~ c.M*1 + a.MM*XM.10 + p.FM*XF.10

YF.1 ~ c.F*1 + a.FF*XF.1 + p.MF*XM.1 
YF.2 ~ c.F*1 + a.FF*XF.2 + p.MF*XM.2
YF.3 ~ c.F*1 + a.FF*XF.3 + p.MF*XM.3
YF.4 ~ c.F*1 + a.FF*XF.4 + p.MF*XM.4
YF.5 ~ c.F*1 + a.FF*XF.5 + p.MF*XM.5
YF.6 ~ c.F*1 + a.FF*XF.6 + p.MF*XM.6
YF.7 ~ c.F*1 + a.FF*XF.7 + p.MF*XM.7
YF.8 ~ c.F*1 + a.FF*XF.8 + p.MF*XM.8
YF.9 ~ c.F*1 + a.FF*XF.9 + p.MF*XM.9
YF.10 ~ c.F*1 + a.FF*XF.10 + p.MF*XM.10

# residual structure: Outcomes
YM.1 ~~ varM*YM.1
YM.2 ~~ varM*YM.2
YM.3 ~~ varM*YM.3
YM.4 ~~ varM*YM.4
YM.5 ~~ varM*YM.5
YM.6 ~~ varM*YM.6
YM.7 ~~ varM*YM.7
YM.8 ~~ varM*YM.8
YM.9 ~~ varM*YM.9
YM.10 ~~ varM*YM.10

YF.1 ~~ varF*YF.1
YF.2 ~~ varF*YF.2
YF.3 ~~ varF*YF.3
YF.4 ~~ varF*YF.4
YF.5 ~~ varF*YF.5
YF.6 ~~ varF*YF.6
YF.7 ~~ varF*YF.7
YF.8 ~~ varF*YF.8
YF.9 ~~ varF*YF.9
YF.10 ~~ varF*YF.10
'
```

## Simulation-based power analysis using SEM

Functions for conducting simulation-based power analysis for the L-APIM using SEM 

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# We first create a function to simulate data from the L-APIM model and estimate the model using SEM

summary.LAPIM.SEM = function(model_LAPIM_Parameters,model_LAPIM,N.dyad){

data.wide = simulateData(model_LAPIM_Parameters, sample.nobs=N.dyad)
fit_LAPIM = sem(model_LAPIM,data = data.wide)
summary_fit_LAPIM = parameterEstimates(fit_LAPIM)
summary_fit_LAPIM = data.frame(summary_fit_LAPIM)

# Obtain p-value
p.values.list = summary_fit_LAPIM$pvalue
names(p.values.list) = summary_fit_LAPIM$label
p.values.list = p.values.list[-which(is.na(p.values.list)==TRUE)]

# Obtain estimated effects
estimate.list = summary_fit_LAPIM$est
names(estimate.list) = summary_fit_LAPIM$label
estimate.list = estimate.list[-which(summary_fit_LAPIM$label=='')]

return(list(summary.SEM=summary_fit_LAPIM,p.values=p.values.list,estimates=estimate.list))
}

# Function for conducting the simulation based power analysis

Power.sim.LAPIM.SEM = function(model_LAPIM_Parameters,model_LAPIM,N.dyad,alpha,R){

# We perform the Monte Carlo simulation
# Set the session to use parallel computing
plan(multisession)

# Estimate model
Simulation.LAPIM.SEM = future_lapply(1:R, function(r) summary.LAPIM.SEM(model_LAPIM_Parameters,model_LAPIM,N.dyad),
future.seed = 0xBEEF)

# Obtain matrix for computing power
Simulation.LAPIM.SEM.power = lapply(1:R, function(r) Simulation.LAPIM.SEM[[r]]$p.values<alpha)
Simulation.LAPIM.SEM.power = matrix(unlist(Simulation.LAPIM.SEM.power), nrow = R, byrow = TRUE)
# Obtain power
Power.LAPIM.SEM = colMeans(Simulation.LAPIM.SEM.power)
names(Power.LAPIM.SEM) = names(Simulation.LAPIM.SEM[[1]]$p.values)
# Obtain std. error of power
Power.se.LAPIM.SEM = sqrt(Power.LAPIM.SEM*(1-Power.LAPIM.SEM)/R)
names(Power.se.LAPIM.SEM) = names(Power.LAPIM.SEM)
  
# Obtain matrix with the estimated effects in each replicate
Simulation.LAPIM.SEM.estimates = lapply(1:R, function(r) Simulation.LAPIM.SEM[[r]]$estimates)
Simulation.LAPIM.SEM.estimates = matrix(unlist(Simulation.LAPIM.SEM.estimates), nrow = R, byrow = TRUE)

# Obtain average estimated effect
Estimate.LAPIM.SEM = colMeans(Simulation.LAPIM.SEM.estimates)
names(Estimate.LAPIM.SEM) = names(Simulation.LAPIM.SEM[[1]]$estimates)
# Obtain std. error of power
Estimate.se.LAPIM.SEM = apply(Simulation.LAPIM.SEM.estimates,2,sd)/sqrt(R)
names(Estimate.se.LAPIM.SEM) = names(Estimate.LAPIM.SEM)

return(list(Power.LAPIM.SEM = Power.LAPIM.SEM, Power.se.LAPIM.SEM=Power.se.LAPIM.SEM,
            Estimate.LAPIM.SEM = Estimate.LAPIM.SEM, Estimate.se.LAPIM.SEM=Estimate.se.LAPIM.SEM))
}

```

We simulate data using lavaan and we estimate L-APIM using SEM, and we compute power:

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Parameters of the Monte Carlo simulation
R = 1000
alpha = 0.05
N.dyad = c(60,80,100,160,200,300)

# Conduct the simulation-based power analysis
Simulation.Power.LAPIM.SEM = future_lapply(1:length(N.dyad), function(i) Power.sim.LAPIM.SEM(model_LAPIM_Parameters,model_LAPIM,N.dyad[i],alpha,R),
future.seed = 0xBEEF)

# Obtain the average effect of the estimated coefficients and power
Coef.LAPIM.SEM.names = c('c.F','c.M','a.FF','p.MF','a.MM','p.FM') 
Coef.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.LAPIM.SEM.names))
Coef.se.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.LAPIM.SEM.names))
Power.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.LAPIM.SEM.names))
Power.se.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.LAPIM.SEM.names))
for (i in 1:length(N.dyad)){
Coef.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Estimate.LAPIM.SEM[Coef.LAPIM.SEM.names]
Coef.se.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Estimate.se.LAPIM.SEM[Coef.LAPIM.SEM.names]
Power.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Power.LAPIM.SEM[Coef.LAPIM.SEM.names]
Power.se.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Power.se.LAPIM.SEM[Coef.LAPIM.SEM.names]
}

colnames(Coef.LAPIM.SEM) = colnames(Coef.se.LAPIM.SEM) = colnames(Power.LAPIM.SEM) = colnames(Power.se.LAPIM.SEM) = c('c.F','c.M','a.FF','p.MF','a.MM','p.FM')

rownames(Coef.LAPIM.SEM) = rownames(Coef.se.LAPIM.SEM) = rownames(Power.LAPIM.SEM) = rownames(Power.se.LAPIM.SEM) = N.dyad

# Estimated power
kable(Power.LAPIM.SEM, format = "markdown", digits = 2)
# Standard error of the estimated power
kable(Power.se.LAPIM.SEM, format = "markdown", digits = 2)
# Estimated effect
kable(Coef.LAPIM.SEM, format = "markdown", digits = 2)
# Standard error of the estimated power
kable(Coef.se.LAPIM.SEM, format = "markdown", digits = 2)

# Variance components
# Obtain the average estimated variance components
Coef.var.LAPIM.SEM.names = c('varF','varM','ivarB','ivarA','iA') 
Coef.var.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.var.LAPIM.SEM.names))
Coef.var.se.LAPIM.SEM = matrix(0,length(N.dyad),length(Coef.var.LAPIM.SEM.names))
for (i in 1:length(N.dyad)){
Coef.var.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Estimate.LAPIM.SEM[Coef.var.LAPIM.SEM.names]
Coef.var.se.LAPIM.SEM[i,] = Simulation.Power.LAPIM.SEM[[i]]$Estimate.se.LAPIM.SEM[Coef.var.LAPIM.SEM.names]
}

colnames(Coef.var.LAPIM.SEM) = colnames(Coef.var.se.LAPIM.SEM) =  c('sigma2.eps.F','sigma2.eps.M','sigma2.nu.F','sigma2.nu.M','cov.nu.F.M')

rownames(Coef.var.LAPIM.SEM) = rownames(Coef.var.se.LAPIM.SEM) = N.dyad

# Estimated effect of the variance components
kable(Coef.var.LAPIM.SEM, format = "markdown", digits = 2)
# Standard error of the variance components
kable(Coef.var.se.LAPIM.SEM, format = "markdown", digits = 2)

```

# Simulation-based power analysis using PowerLAPIM

Next, we use the application PowerLAPIM to conduct the simulation-based power analysis. We select the population model of interest (i.e., Model 1). We indicate that we want to consider the following values for the number of dyads: 60, 80, 100, 160, 200, and 300. We set the number of measurements within each participant to 10. We fill in values for the model parameters and we indicate that the predictors (i.e., enacted response) should be person-mean centered. We set the Type I error, α, to .05 and the number of Monte Carlo replicates to 1,000, and we choose the Maximizing the restricted log-likelihood option when specifying the estimation method. Finally, we click on Compute Power.

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# We set the parameter values of Model 9
Model = 1
N.dyad = c("60","80","100","160","200","300")
N0.dyad = NULL
N1.dyad = NULL
T.obs = 10  
c.F = 39.243
c.M = 40.682
a.FF = 0.283
p.MF = 0.061
a.FF2 = NULL
p.MF2 = NULL 
a.MM = 0.279
p.FM = 0.074
a.MM2 = NULL
p.FM2 = NULL 
c = NULL
a = NULL
a.2 = NULL
p = NULL
p.2 = NULL                             
c.F0 = NULL
c.F1 = NULL
c.M0 = NULL
c.M1 = NULL
a.FF0 = NULL
a.FF1 = NULL
a.FF02 = NULL
a.FF12 = NULL
p.MF0 = NULL
p.MF1 = NULL
p.MF02 = NULL
p.MF12 = NULL
a.MM0 = NULL
a.MM1 = NULL
a.MM02 = NULL
a.MM12 = NULL
p.FM0 = NULL
p.FM1 = NULL
p.FM02 = NULL
p.FM12 = NULL
c0 = NULL
c1 = NULL
a0 = NULL
a1 = NULL
a02 = NULL
a12 = NULL
p0 = NULL
p1 = NULL
p02 = NULL
p12 = NULL
b.F = NULL
b.M = NULL
b.FF = NULL
b.MF = NULL
b.MM = NULL
b.FM = NULL
b.FF2 = NULL
b.MF2 = NULL
b.MM2 = NULL
b.FM2 = NULL
d.F = NULL
d.M = NULL
d.FF = NULL
d.MF = NULL
d.MM = NULL
d.FM = NULL
d.FF2 = NULL
d.MF2 = NULL
d.MM2 = NULL
d.FM2 = NULL
b = NULL
b.a = NULL
b.a2 = NULL
b.p = NULL
b.p2 = NULL
d = NULL
d.a = NULL
d.a2 = NULL
d.p = NULL
d.p2 = NULL
rho.YF = NULL
rho.YM = NULL
rho.Y = NULL
rho.YF0 = NULL
rho.YF1 = NULL
rho.YM0 = NULL
rho.YM1 = NULL
sigma.eps.F = sqrt(223.108)
sigma.eps.M = sqrt(257.404)
rho.eps.FM = 0
sigma.nu.F = sqrt(101.541)
sigma.nu.M = sqrt(76.356)
rho.nu.F.M = 30.684/(sigma.eps.F*sigma.eps.M)
sigma.nu = NULL
mu.XF = 74.922
sigma.XF = sqrt(360.089)
mu.XM = 74.689
sigma.XM = sqrt(331.517)
rho.X = 0
mu.XF0 = NULL
mu.XF1 = NULL
sigma.XF0 = NULL
sigma.XF1 = NULL
mu.XM0 = NULL
mu.XM1 = NULL
sigma.XM0 = NULL
sigma.XM1 = NULL
rho.X0 = NULL
rho.X1 = NULL
mu.W = NULL
sigma.W = NULL
prob.D = NULL
is.center.X = TRUE
is.center.W = NULL
R = 1000
alpha = 0.05
is.REML = FALSE
```

## Conduct power analysis using PowerLAPIM

```{r, echo=TRUE, warning=FALSE, eval=TRUE}
# Conduct power analysis
Fit.Model.LAPIM = Sim.model.Dyad.IL(Model,N.dyad,N0.dyad,N1.dyad,T.obs,  
c.F,c.M,a.FF,p.MF,a.FF2,p.MF2,a.MM,p.FM,a.MM2,p.FM2,
c,a,a.2,p,p.2,
c.F0,c.F1,c.M0,c.M1,a.FF0,a.FF1,a.FF02,a.FF12,p.MF0,p.MF1,p.MF02,p.MF12,
a.MM0,a.MM1,a.MM02,a.MM12,p.FM0,p.FM1,p.FM02,p.FM12,
c0,c1,a0,a1,a02,a12,p0,p1,p02,p12,
b.F,b.M,b.FF,b.MF,b.MM,b.FM,b.FF2,b.MF2,b.MM2,b.FM2,
d.F,d.M,d.FF,d.MF,d.MM,d.FM,d.FF2,d.MF2,d.MM2,d.FM2,
b,b.a,b.a2,b.p,b.p2,
d,d.a,d.a2,d.p,d.p2,
rho.YF,rho.YM,rho.Y,rho.YF0,rho.YF1,rho.YM0,rho.YM1,
sigma.eps.F,sigma.eps.M,rho.eps.FM,
sigma.nu.F,sigma.nu.M,rho.nu.F.M,sigma.nu,
mu.XF,sigma.XF,mu.XM,sigma.XM,rho.X,
mu.XF0,mu.XF1,sigma.XF0,sigma.XF1,mu.XM0,mu.XM1,sigma.XM0,sigma.XM1,rho.X0,rho.X1,
mu.W,sigma.W,prob.D,
is.center.X,is.center.W,R,alpha,is.REML)

# Simulation results for the power curve
kable(Fit.Model.LAPIM$power.curve, format = "markdown", digits = 2)

# Simulation results for the fixed effects
kable(Fit.Model.LAPIM$coef.sim, format = "markdown", digits = 2)

# Simulation results for the variance components
kable(Fit.Model.LAPIM$cov.sim, format = "markdown", digits = 2)
```